Implementation and Analysis of Homomorphic Facial Image Encryption and Manipulation

### 2019-01-11 paper/PCSC2019-sigconf.tex
Final paper done

\author{Me 1}
\affiliation{%
  \institution{Institute for Clarity in Documentation}
  \streetaddress{P.O. Box 1212}
  \city{Dublin}
  \state{Ohio}
  \postcode{43017-6221}
}
\email{webmaster@marysville-ohio.com}

\author{Me 2}
\affiliation{%
  \institution{The Th{\o}rv{\"a}ld Group}
  \streetaddress{1 Th{\o}rv{\"a}ld Circle}
  \city{Hekla}
  \country{Iceland}}
\email{larst@affiliation.org}

% The default list of authors is too long for headers.
\renewcommand{\shorttitle}{Impl. and Analysis of Homomorphic Facial Image Encryption and Manipulation}
% \renewcommand{\shortauthors}{B. Trovato et al.}

@@

\keywords{homomorphic encryption, image operations, facial recognition, numerical approximations}

@@

\begin{acks}
  The authors would like to thank Dr. Yuhua Li for providing the
  MATLAB code of the \textit{BEPS} method. Testing testing.

  The authors would also like to thank the anonymous referees for
  their valuable comments and helpful suggestions. The work is
  supported by the \grantsponsor{GS501100001809}{National Natural
    Science Foundation of
    China}{http://dx.doi.org/10.13039/501100001809} under Grant
  No.:~\grantnum{GS501100001809}{61273304}
  and~\grantnum[http://www.nnsf.cn/youngscientists]{GS501100001809}{Young
    Scientists' Support Program}.

\end{acks}

>>>>

\author{Aldrich Ellis C. Asuncion}
\affiliation{%
  \institution{Ateneo de Manila University}
  \streetaddress{Katipunan Avenue, Loyola Heights}
  \city{Quezon City}
  \country{Philippines}
  \postcode{1108}
}
\email{aldrich.asuncion@obf.ateneo.edu}

\author{Brian Christopher T. Guadalupe}
\affiliation{%
  \institution{Ateneo de Manila University}
  \streetaddress{Katipunan Avenue, Loyola Heights}
  \city{Quezon City}
  \country{Philippines}
  \postcode{1108}
}
\email{brian.guadalupe@obf.ateneo.edu}

% The default list of authors is too long for headers.
\renewcommand{\shorttitle}{Impl. and Analysis of Homomorphic Facial Image Encryption and Manipulation}
\renewcommand{\shortauthors}{A. Asuncion and B. Guadalupe}

@@

\keywords{cryptography, homomorphic encryption, data privacy, image processing, intensity transformation, facial recognition, numerical approximations}

@@

\begin{acks}
We would like to thank our adviser Dr. William Emmanuel S. Yu for his guidance and constant feedback, and our panelists Dr. Andrei D. Coronel and Dr. Mari-jo P. Ruiz for lending their expertise and for giving their invaluable comments and insights.
Due acknowlegement is also given to the University of Essex for making the \texttt{faces94} dataset publicly available for research purposes.
\end{acks}

### 2019-01-11 paper/appendix.tex
Final paper done

\section{Correction for Dasgupta--Pal}
\label{chap:correction}
\subsection{Bitwise Description of the Dasgupta--Pal Cryptosystem}
The Dasgupta--Pal cryptosystem \cite{dasgupta_design_2016} encrypts each bit in a bit string independently.
In terms of the encryption of a single bit, the Dasgupta--Pal cryptosystem can be described as follows:
\begin{description}
	\item[Key generation]
	Let the secret key, $S_k$ be a large prime.
	Let the public refresh key, $R_k$, be $S_k \times z$, where $z$ is a large even integer.
	\item[Encryption]
	Given a message $m$, the encryption function is defined as
	\begin{align*}
		E(m) = m + S_kr
	\end{align*}
	where $r$ is a random integer.
	\item[Decryption]
	Given a ciphertext $c$, the decryption function is defined as
	\begin{align*}
		D(c) = c \bmod S_k \bmod 2
	\end{align*}
\end{description}
The homomorphic operations are then defined as
\begin{description}
	\item[\textsc{xor} on ciphertexts]
	\begin{align*}
		D(E(a)+E(b)) = a \textsc{ xor } b = (a + b) \bmod 2
	\end{align*}
	\item[\textsc{and} on ciphertexts]
	\begin{align*}
		D(E(a)\times E(b)) = a \textsc{ and } b = ab \bmod 2
	\end{align*}
\end{description}
After repeated operations on ciphertexts, the resulting ciphertext can grow in magnitude.
To prevent storage issues and keep the ciphertext size small, a refresh function is used.
\begin{description}
	\item[Refresh function]
	Given a ciphertext $c$, the refresh function is defined as
	\begin{align*}
		R(c) = c \bmod R_k
	\end{align*}
\end{description}
\subsection{Cases Where Decryption Fails}
We consider the following quantity:
\begin{align}
	\label{eq:cornercase_ciphertext}
	D(\underbrace{E(1)+E(1)+\cdots+E(1)}_{S_k \text{ times}}).
\end{align}
Since $S_k$ is odd, the corresponding operation in the plaintext space is
\begin{align*}
	\label{eq:cornercase_plaintext}
	\underbrace{1 \textsc{ xor } 1 \textsc{ xor } \cdots \textsc{ xor } 1}_{S_k \text{ times}} = 1.
\end{align*}
However, evaluating Equation \ref{eq:cornercase_ciphertext} yields:
\begin{align*}
	D(\underbrace{E(1)+E(1)+\cdots+E(1)}_{S_k \text{ times}})
	&= D\left(\sum_{i=1}^{S_k}{(1+S_kr_i)}\right)\\
	&= D\left(S_k + S_k\sum_{i=1}^{S_k}{r_i}\right)\\
	&= \left(S_k + S_k\sum_{i=1}^{S_k}{r_i}\right) \bmod S_k \bmod 2\\
	&= 0 \bmod 2\\
	&= 0.
\end{align*}
Since $\underbrace{1 \textsc{ xor } 1 \textsc{ xor } \cdots \textsc{ xor } 1}_{S_k \text{ times}} = 1\neq 0 = D(\underbrace{E(1)+E(1)+\cdots+E(1)}_{S_k \text{ times}})$, we have shown an instance where incorrect decryption occurs given a sequence of operations on ciphertexts.

@@

This integral can be approximated using the five-point Gauss-Legendre quadrature rule \cite{kythe_quadrature_2002}. We first convert the integral to an integral over the interval $[-1,1]$ using the following transformation:
\begin{align*}
	\int_a^b{f(x)\diff x}
	&= \frac{b-a}{2}\int_{-1}^{1}{f\left(\frac{b-a}{2}x+\frac{a+b}{2}\right)\diff x}.
\end{align*}
Then, we approximate the integral using the following summation:
\begin{align*}
  \int_{-1}^{1}{f(x)\diff x} &= \sum_{i=1}^{5}{w_if(x_i)},
\end{align*}
where
\begin{multicols}{2}
	\noindent
	\begin{align*}
		w_1 &= 0\\
		w_2 &= \frac{1}{21}\sqrt{245-14\sqrt{70}}\\
		w_3 &= -\frac{1}{21}\sqrt{245-14\sqrt{70}}\\
		w_4 &= \frac{1}{21}\sqrt{245+14\sqrt{70}}\\
		w_5 &= -\frac{1}{21}\sqrt{245+14\sqrt{70}}
	\end{align*}
	\columnbreak
	\begin{align*}
		x_1 &= \frac{128}{225}\\
		x_2 &= \frac{1}{900}\left( 322 + 13\sqrt{70}\right)\\
		x_3 &= \frac{1}{900}\left( 322 + 13\sqrt{70}\right)\\
		x_4 &= \frac{1}{900}\left( 322 - 13\sqrt{70}\right)\\
		x_5 &= \frac{1}{900}\left( 322 - 13\sqrt{70}\right)
	\end{align*}
\end{multicols}
Applying this procedure to the integral in equation \ref{eq:log_integral} using SageMath 8.3 yields the following approximation:
\begin{equation}\label{eq:standardquadrature}
  \log(1+x) \approx
  \frac{137x^5 + 2310x^4 + 9870x^3 + 15120x^2 + 7560x}
  {30x^5 + 900x^4 + 6300x^3 + 16800x^2 + 18900x + 7560}.
\end{equation}

@@

Applying the five-point Gauss-Legendre quadrature rule with $\alpha = 1/20$ using SageMath 8.3, we arrive at the approximation:
\begin{align}\label{eq:scaledquadrature}
  \begin{split}
    &\log(1+x) \\
    &\approx \frac{137x^5 + 33185x^4 + 931370x^3 - 13403630x^2 - 289469315x - 713567363}
    {30(x^5 + 505x^4 + 42010x^3 + 923010x^2 + 5722005x + 8040501)} \\
    &+ \log{20}
  \end{split}
\end{align}

>>>>

\section{Correction for Dasgupta--Pal}
\label{chap:correction}
\subsection{Bitwise Description of the Dasgupta--Pal Cryptosystem}
The Dasgupta--Pal cryptosystem \cite{dasgupta_design_2016} encrypts each bit in a bit string independently.
In terms of the encryption of a single bit, the Dasgupta--Pal cryptosystem can be described as follows:
\begin{description}
	\item[Key generation]
	Let the secret key, $S_k$ be a large prime.
	Let the public refresh key, $R_k$, be $S_k \times z$, where $z$ is a large even integer.
	\item[Encryption]
	Given a message $m$, the encryption function is defined as
	\begin{align*}
		E(m) = m + S_kr
	\end{align*}
	where $r$ is a random integer.
	\item[Decryption]
	Given a ciphertext $c$, the decryption function is defined as
	\begin{align*}
		D(c) = c \bmod S_k \bmod 2
	\end{align*}
\end{description}

The homomorphic operations are then defined as
\begin{description}
	\item[\textsc{xor} on ciphertexts]
	\begin{align*}
		D(E(a)+E(b)) = a \textsc{ xor } b = (a + b) \bmod 2
	\end{align*}
	\item[\textsc{and} on ciphertexts]
	\begin{align*}
		D(E(a)\times E(b)) = a \textsc{ and } b = ab \bmod 2
	\end{align*}
\end{description}

After repeated operations on ciphertexts, the resulting ciphertext can grow in magnitude.
To prevent storage issues and keep the ciphertext size small, a refresh function is used.
\begin{description}
	\item[Refresh function]
	Given a ciphertext $c$, the refresh function is defined as
	\begin{align*}
		R(c) = c \bmod R_k
	\end{align*}
\end{description}
\subsection{Cases Where Decryption Fails}
We consider the following quantity:
\begin{align}
	\label{eq:cornercase_ciphertext}
	D(\underbrace{E(1)+E(1)+\cdots+E(1)}_{S_k \text{ times}}).
\end{align}

Since $S_k$ is odd, the corresponding operation in the plaintext space is
\begin{align*}
	\label{eq:cornercase_plaintext}
	\underbrace{1 \textsc{ xor } 1 \textsc{ xor } \cdots \textsc{ xor } 1}_{S_k \text{ times}} = 1.
\end{align*}

However, evaluating Equation \ref{eq:cornercase_ciphertext} yields:
\begin{align*}
	D(\underbrace{E(1)+E(1)+\cdots+E(1)}_{S_k \text{ times}})
	&= D\left(\sum_{i=1}^{S_k}{(1+S_kr_i)}\right)\\
	&= D\left(S_k + S_k\sum_{i=1}^{S_k}{r_i}\right)\\
	&= \left(S_k + S_k\sum_{i=1}^{S_k}{r_i}\right) \bmod S_k \bmod 2\\
	&= 0 \bmod 2\\
	&= 0.
\end{align*}
Since $\underbrace{1 \textsc{ xor } 1 \textsc{ xor } \cdots \textsc{ xor } 1}_{S_k \text{ times}} = 1\neq 0 = D(\underbrace{E(1)+E(1)+\cdots+E(1)}_{S_k \text{ times}})$, we have shown an instance where incorrect decryption occurs given a sequence of operations on ciphertexts.

@@

This integral can be approximated using the five-point Gauss--Legendre quadrature rule \cite{kythe_quadrature_2002}. We first convert the integral to an integral over the interval $[-1,1]$ using the following transformation:
\begin{align*}
	\int_a^b{f(x)\diff x}
	&= \frac{b-a}{2}\int_{-1}^{1}{f\left(\frac{b-a}{2}x+\frac{a+b}{2}\right)\diff x}.
\end{align*}
Then, we approximate the integral using the following summation:
\begin{align*}
  \int_{-1}^{1}{f(x)\diff x} &= \sum_{i=1}^{5}{w_if(x_i)},
\end{align*}
where
\begin{multicols}{2}
	\noindent
	\begin{align*}
		w_1 &= 0\\
		w_2 &= \frac{1}{21}\sqrt{245-14\sqrt{70}}\\
		w_3 &= -\frac{1}{21}\sqrt{245-14\sqrt{70}}\\
		w_4 &= \frac{1}{21}\sqrt{245+14\sqrt{70}}\\
		w_5 &= -\frac{1}{21}\sqrt{245+14\sqrt{70}}
	\end{align*}
	\columnbreak
	\begin{align*}
		x_1 &= \frac{128}{225}\\
		x_2 &= \frac{1}{900}\left( 322 + 13\sqrt{70}\right)\\
		x_3 &= \frac{1}{900}\left( 322 + 13\sqrt{70}\right)\\
		x_4 &= \frac{1}{900}\left( 322 - 13\sqrt{70}\right)\\
		x_5 &= \frac{1}{900}\left( 322 - 13\sqrt{70}\right)
	\end{align*}
\end{multicols}
Applying this procedure to the integral in equation \ref{eq:log_integral} using SageMath 8.3 yields the following approximation:
\begin{equation}\label{eq:standardquadrature}
  \log(1+x) \approx
  \frac{137x^5 + 2310x^4 + 9870x^3 + 15120x^2 + 7560x}
  {30x^5 + 900x^4 + 6300x^3 + 16800x^2 + 18900x + 7560}.
\end{equation}

@@

Applying the five-point Gauss--Legendre quadrature rule with $\alpha = 1/20$ using SageMath 8.3, we arrive at the approximation:
\begin{align}\label{eq:scaledquadrature}
  \begin{split}
    &\log(1+x) \\
    &\approx \frac{137x^5 + 33185x^4 + 931370x^3 - 13403630x^2 - 289469315x - 713567363}
    {30(x^5 + 505x^4 + 42010x^3 + 923010x^2 + 5722005x + 8040501)} \\
    &+ \log{20}
  \end{split}
\end{align}

### 2019-01-11 paper/paper-conf.tex
Final paper done

\begin{table*}
	\caption{Comparison of intensity transformations under Dasgupta--Pal}
	\label{tbl:it-dp}
	\begin{tabular}{m{1cm}*{7}{>{\centering\arraybackslash}m{1.75cm}}}
		\toprule
		\multirow{2}{*}{Image} & \multirow{2}{*}{Original} & \multicolumn{2}{c}{Image negation} & \multicolumn{2}{c}{Logarithm transformation} & \multicolumn{2}{c}{Power-law transformation} \\
							   &                           & PDT           & CDT          & PDT            & CDT           & PDT               & CDT           \\ 
		\midrule
		\xintFor #1 in {anpage, bplyce, drbost, ksunth, martin, pmives, rnpwil, sbains, swewin, yfhsie} \do {%
		\texttt{#1} & \includegraphics[width=1.75cm]{out_faces/dp_negate_#1_original.png} & \includegraphics[width=1.75cm]{out_faces/dp_negate_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dp_negate_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/dp_logtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dp_logtransform_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/paillier_pwrtransform_#1_reference.png} &  \\ }%
		\bottomrule         
	\end{tabular}
\end{table*}

@@

\subsubsection{Power-Law Transformation}
Unlike in the previous intensity transformations, applying the power-law transformation under both cryptosystems produced less than accurate images. The accuracy varies greatly across all the images as in the case of Paillier, with mean squared errors as high as 8270.696 and as low as 616.419, and SSIM scores ranging from 0.43185 to 0.92334. As expected, the total processing time now takes about 20 seconds per image since the power-law transformation is more computationally intensive due to its approximation of an infinite series consisting of terms using the logarithm function, which is also approximated using a combination of addition and multiplication operations.

\begin{table}[h]
	\caption{Power-law transformation under Paillier}
	\label{tbl:pwr-pal}
    \begin{tabular}{lcccccc}
        \toprule
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
        \texttt{anpage} & 3910.678 & 12.208 & 0.46712 & 0.099 & 14.695 & 0.024 \\
		\texttt{bplyce} & 873.064 & 18.720 & 0.84379 & 0.139 & 16.190 & 0.023 \\
		\texttt{drbost} & 1261.059 & 17.123 & 0.77229 & 0.082 & 13.866 & 0.023 \\
		\texttt{ksunth} & 653.049 & 19.981 & 0.90673 & 0.083 & 15.507 & 0.023 \\
		\texttt{martin} & 646.310 & 20.026 & 0.88157 & 0.108 & 15.727 & 0.045 \\
		\texttt{pmives} & 2047.933 & 15.018 & 0.69408 & 0.113 & 14.728 & 0.034 \\
		\texttt{rnpwil} & 806.473 & 19.065 & 0.85346 & 0.082 & 14.253 & 0.024 \\
		\texttt{sbains} & 616.419 & 20.232 & 0.92334 & 0.121 & 14.415 & 0.023 \\
		\texttt{swewin} & 8270.696 & 8.955 & 0.43185 & 0.112 & 14.362 & 0.065 \\
		\texttt{yfhsie} & 1715.478 & 15.787 & 0.73857 & 0.145 & 20.239 & 0.023 \\
		\bottomrule
        \end{tabular}
\end{table}
\begin{table}[h]
	\caption{Power-law transformation under Dasgupta--Pal}
	\label{tbl:pwr-dp}
    \begin{tabular}{lcccccc}
        \toprule
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
		% \texttt{anpage} & 25115.891 & 4.131 & 0.00000 & 0.016 & 741.872 & 0.031 \\ 10x10
		\texttt{anpage} & 25008.723 & 4.150 & 0.00000 & 0.376 & 9700.926 & 1.269 \\
		% \texttt{bplyce} & 22777.187 & 4.556 & 0.00000 & 0.017 & 730.873 & 0.003 \\ 10x10
		\texttt{bplyce} & 22700.522 & 4.570 & 0.00000 & 0.230 & 9196.609 & 0.043 \\
		% \texttt{drbost} & 18899.906 & 5.366 & 0.00000 & 0.014 & 733.409 & 0.003 \\
		\texttt{drbost} & 18902.214 & 5.366 & 0.00000 & 0.064 & 2261.407 & 0.110 \\ % 20x18
		\texttt{ksunth} & 12585.729 & 7.132 & 0.00000 & 0.044 & 2259.010 & 0.011 \\ % 20x18
		\texttt{martin} & 17012.423 & 5.823 & 0.00000 & 0.066 & 2440.351 & 0.011 \\
		\texttt{pmives} & 31124.615 & 3.200 & 0.00000 & 0.072 & 2492.149 & 0.012 \\
		\texttt{rnpwil} & 22982.917 & 4.517 & 0.00000 & 0.076 & 2321.928 & 0.008 \\
		\texttt{sbains} & 13469.155 & 6.837 & 0.00000 & 0.044 & 2233.818 & 0.008 \\
		\texttt{swewin} & 37453.834 & 2.396 & 0.00000 & 0.049 & 2203.045 & 0.008 \\
		\texttt{yfhsie} & 23037.762 & 4.506 & 0.00000 & 0.045 & 2210.393 & 0.008 \\
		\bottomrule
        \end{tabular}
\end{table}

\section{Conclusion}
In this paper, we have assessed the feasibility and practicality of various homomorphic cryptosystems with regard to secure processing and manipulation of facial image data through creation of a software library that facilitates image processing operations within the encrypted domain, as well as our own implementation of some homomorphic cryptosystems like Dasgupta--Pal for which existing third-party library dedicated for this purpose is not yet available.

This paper also proposes a correction to the Dasgupta--Pal cryptosystem which is further explained in Appendix~\ref{chap:correction}.

@@

Preliminary results have shown that both Paillier and Dasgupta--Pal apply image negation accurately and efficiently, as evidenced by the perfect zero MSE and infinite PSNR. For the logarithm transformation, Paillier was faster and accurate enough (with $\text{MSE} \le 30$ and $\text{SSIM} \approx 0.99$), but Dasgupta--Pal was slower but more accurate (with $\text{MSE} \le 0.01$ and $\text{SSIM} \approx 0.99999$) which was rather unexpected. However both Paillier and Dasgupta--Pal fail to produce accurate results in applying the power-law transformation. Based from these results, the Paillier cryptosystem is consistent enough to produce reasonable to accurate results.

@@

\subsection{Ongoing and Future Work}
Testing intensity transformations under the BGV cryptosystem will be started once the Pyfhel library is deemed stable enough to use, or another Python library that implements BGV becomes available. 
One of the authors has already informed the developers of the Pyfhel library about a bug involving exponentiation of two real numbers.

>>>>

\begin{table*}
	\caption{Comparison of intensity transformations under Dasgupta--Pal}
	\label{tbl:it-dp}
	\begin{tabular}{m{1cm}*{7}{>{\centering\arraybackslash}m{1.75cm}}}
		\toprule
		\multirow{2}{*}{Image} & \multirow{2}{*}{Original} & \multicolumn{2}{c}{Image negation} & \multicolumn{2}{c}{Logarithm transformation} & \multicolumn{2}{c}{Power-law transformation} \\
							   &                           & PDT           & CDT          & PDT            & CDT           & PDT               & CDT           \\ 
		\midrule
		\xintFor #1 in {anpage, bplyce, drbost, ksunth, martin, pmives, rnpwil, sbains, swewin, yfhsie} \do {%
		\texttt{#1} & \includegraphics[width=1.75cm]{out_faces/dp_negate_#1_original.png} & \includegraphics[width=1.75cm]{out_faces/dp_negate_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dp_negate_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/dp_logtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dp_logtransform_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/paillier_pwrtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dp_pwrtransform_#1_decrypted.png} \\ }%
		\bottomrule         
	\end{tabular}
\end{table*}

@@

\subsubsection{Power-Law Transformation}
Applying the power-law transformation under both cryptosystems produced less than accurate images. The accuracy varies greatly across all the images as in the case of Paillier, with mean squared errors as high as 8270.696 and as low as 616.419, and SSIM scores ranging from 0.43185 to 0.92334, as seen in Table~\ref{tbl:pwr-pal}. As expected, the total processing time now takes about 15 to 20 seconds per image since the power-law transformation is more computationally intensive due to its approximation of an infinite series consisting of terms using the logarithm function, which is also approximated using a combination of addition and multiplication operations.

\begin{table}[h]
	\caption{Power-law transformation under Paillier}
	\label{tbl:pwr-pal}
    \begin{tabular}{lcccccc}
        \toprule
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
        \texttt{anpage} & 3910.678 & 12.208 & 0.46712 & 0.099 & 14.695 & 0.024 \\
		\texttt{bplyce} & 873.064 & 18.720 & 0.84379 & 0.139 & 16.190 & 0.023 \\
		\texttt{drbost} & 1261.059 & 17.123 & 0.77229 & 0.082 & 13.866 & 0.023 \\
		\texttt{ksunth} & 653.049 & 19.981 & 0.90673 & 0.083 & 15.507 & 0.023 \\
		\texttt{martin} & 646.310 & 20.026 & 0.88157 & 0.108 & 15.727 & 0.045 \\
		\texttt{pmives} & 2047.933 & 15.018 & 0.69408 & 0.113 & 14.728 & 0.034 \\
		\texttt{rnpwil} & 806.473 & 19.065 & 0.85346 & 0.082 & 14.253 & 0.024 \\
		\texttt{sbains} & 616.419 & 20.232 & 0.92334 & 0.121 & 14.415 & 0.023 \\
		\texttt{swewin} & 8270.696 & 8.955 & 0.43185 & 0.112 & 14.362 & 0.065 \\
		\texttt{yfhsie} & 1715.478 & 15.787 & 0.73857 & 0.145 & 20.239 & 0.023 \\
		\bottomrule
        \end{tabular}
\end{table}

When Dasgupta--Pal was used in the power-law transformation, it completely failed to produce a discernible image and only resulted in a blank image. The mean squared errors for this case is an order of magnitude higher than the results from using Paillier. Furthermore, doing a power-law transformation under Dasgupta--Pal is not only impractical in terms of accuracy, but also it is impractical in terms of time efficiency because it took about 2 hours and 40 minutes on average to process each image.

\begin{table}[h]
	\caption{Power-law transformation under Dasgupta--Pal}
	\label{tbl:pwr-dp}
    \begin{tabular}{lcccccc}
        \toprule
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
		\texttt{anpage} & 25008.723 & 4.150 & 0.00000 & 0.376 & 9700.926 & 1.269 \\
		\texttt{bplyce} & 22700.522 & 4.570 & 0.00000 & 0.230 & 9196.609 & 0.043 \\
		% \texttt{anpage} & 25115.891 & 4.131 & 0.00000 & 0.016 & 741.872 & 0.031 \\ 10x10
		% \texttt{bplyce} & 22777.187 & 4.556 & 0.00000 & 0.017 & 730.873 & 0.003 \\ 10x10
		% \texttt{drbost} & 18899.906 & 5.366 & 0.00000 & 0.014 & 733.409 & 0.003 \\
		\texttt{drbost} & 18902.214 & 5.366 & 0.00000 & 0.277 & 9261.407 & 0.150 \\
		\texttt{ksunth} & 12585.729 & 7.132 & 0.00000 & 0.257 & 9259.010 & 0.051 \\
		\texttt{martin} & 17012.423 & 5.823 & 0.00000 & 0.279 & 9440.351 & 0.051 \\
		\texttt{pmives} & 31124.615 & 3.200 & 0.00000 & 0.285 & 9492.149 & 0.052 \\
		\texttt{rnpwil} & 22982.917 & 4.517 & 0.00000 & 0.289 & 9321.928 & 0.048 \\
		\texttt{sbains} & 13469.155 & 6.837 & 0.00000 & 0.257 & 9233.818 & 0.048 \\
		\texttt{swewin} & 37453.834 & 2.396 & 0.00000 & 0.262 & 9203.045 & 0.048 \\
		\texttt{yfhsie} & 23037.762 & 4.506 & 0.00000 & 0.258 & 9210.393 & 0.048 \\
		% \texttt{drbost} & 18902.214 & 5.366 & 0.00000 & 0.064 & 2261.407 & 0.110 \\ % 20x18
		% \texttt{ksunth} & 12585.729 & 7.132 & 0.00000 & 0.044 & 2259.010 & 0.011 \\ % 20x18
		% \texttt{martin} & 17012.423 & 5.823 & 0.00000 & 0.066 & 2440.351 & 0.011 \\
		% \texttt{pmives} & 31124.615 & 3.200 & 0.00000 & 0.072 & 2492.149 & 0.012 \\
		% \texttt{rnpwil} & 22982.917 & 4.517 & 0.00000 & 0.076 & 2321.928 & 0.008 \\
		% \texttt{sbains} & 13469.155 & 6.837 & 0.00000 & 0.044 & 2233.818 & 0.008 \\
		% \texttt{swewin} & 37453.834 & 2.396 & 0.00000 & 0.049 & 2203.045 & 0.008 \\
		% \texttt{yfhsie} & 23037.762 & 4.506 & 0.00000 & 0.045 & 2210.393 & 0.008 \\
		\bottomrule
        \end{tabular}
\end{table}

\section{Conclusion}
In this paper, we have assessed the feasibility and practicality of various homomorphic cryptosystems with regard to secure processing and manipulation of facial image data through creation of a software library that facilitates image processing operations within the encrypted domain, as well as our own implementation of some homomorphic cryptosystems like Dasgupta--Pal for which existing third-party libraries dedicated for this purpose are not yet available.

% This paper also proposes a correction to the Dasgupta--Pal cryptosystem which is further explained in Appendix~\ref{chap:correction}.

@@

Preliminary results have shown that both Paillier and Dasgupta--Pal apply image negation accurately and efficiently, as evidenced by the perfect zero MSE and infinite PSNR. For the logarithm transformation, Paillier was faster and accurate enough (with $\text{MSE} \le 30$ and $\text{SSIM} \approx 0.99$), but Dasgupta--Pal was slower but more accurate (with $\text{MSE} \le 0.01$ and $\text{SSIM} \approx 0.99999$) which was rather unexpected. However both Paillier and Dasgupta--Pal fail to produce accurate results in applying the power-law transformation, with the latter completely failing to produce discernible results. Based from these results, the Paillier cryptosystem is consistent enough to produce reasonable to accurate results.

@@

\subsection{Ongoing and Future Work}
Testing intensity transformations under the BGV cryptosystem will be started once the Pyfhel library is deemed stable enough to use, or another Python library that implements BGV becomes available. 
One of the authors of this paper has already informed the developers of the Pyfhel library about a bug involving exponentiation of two real numbers.
